Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

\begin{lemma} \label{lmm:hv}
    The H-V $k$-SJ problem can be solved in time
    \myeqn{
        O(k) \cdot \big( F_{k-1}(n, \out) + n\log n + k \cdot \out \big) \nn
    }
    where $n$ (resp., $\out$) is the input (resp., output) size of the problem.
\end{lemma}

@@

>>>>

\begin{lemma} \label{lmm:hv}
    Equipped with the algorithm $\A$ described above, the H-V $k$-SJ problem can be solved in time
    \myeqn{
        O(k) \cdot \big( F_{k-1}(n, \out) + n\log n + k \cdot \out \big) \nn
    }
    where $n$ (resp., $\out$) is the input (resp., output) size of the problem.
\end{lemma}

@@

In the same fashion, we obtain the trimmed version $R_i'$ of $R_i$ for all $i \in [2, n]$, spending $O(k n \log n)$ time in total.
